\documentclass[12pt,a4paper]{article}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{hyperref}

\title{\textbf{Milestone 12 Worksheet}\\Professional Foundations}
\author{Abdulmujeeb Uthman}
\date{September 21, 2025}

\begin{document}

\maketitle

\section*{SECTION A: Introducing Yourself}

\subsection*{Week 9 – GCGO}
\textbf{Chosen GCGO:} Technology \& Innovation \\
\textbf{Why it resonates:} I’m inspired by how emerging technologies can be used to solve problems, protect systems, and create opportunities. Technology \& Innovation drives my passion for cybersecurity, web building, and machine learning exploration.

\subsection*{Week 10 – Specialization \& Career}
\textbf{Specialization:} Cybersecurity (Offensive Security focus) \\
\textbf{Why I chose it:} It allows me to learn by thinking like an attacker, strengthen systems, and directly connect to my GCGO of Technology \& Innovation. \\
\textbf{Ideal Job Title/Position:} Independent Red Team Operator | Offensive Security Researcher \\
\textbf{Top 3 insights from experts (FreeCodeCamp, David Bombal, The Cyber Mentor):}
\begin{enumerate}
    \item Learn by doing --- build labs and projects to develop real skills.
    \item Master fundamentals like networking and Linux, then simulate real environments.
    \item Practice hands-on (CTFs, labs) and document findings to show growth.
\end{enumerate}

\subsection*{Week 11 – Photo / Links / Fun Fact}
\textbf{Professional photo:} *(attach updated professional headshot)* \\
\textbf{Portfolio link:} \href{https://sites.google.com/view/abdulmujeeb-uthman}{My Portfolio} \\
\textbf{LinkedIn:} \href{https://www.linkedin.com/in/abdulmujeeb-uthman/}{Check My Page} \\
\textbf{Fun fact:} I blend creative building (websites, designs) with hacker curiosity — experimenting with both LaTeX and portfolio design before polishing everything into a professional brand.

\subsection*{New Bio}
I’m Abdulmujeeb — a \textbf{Red Team Operator} passionate about offensive security and penetration testing, using real-world attacker techniques to strengthen digital systems. Alongside cybersecurity, I’m also a \textbf{Web Builder} who designs and develops projects with security in mind, and an \textbf{ML Explorer} curious about how machine learning can power the next wave of innovation.  

This mix of offensive security, web development, and ML exploration gives me a unique edge: I don’t just build solutions, I test and refine them against threats. I learn continuously from experts like FreeCodeCamp, David Bombal, and The Cyber Mentor — combining labs, CTFs, and documented projects to sharpen my craft and share my journey.  

Explore my projects and portfolio here:  
\href{https://sites.google.com/view/abdulmujeeb-uthman}{My Portfolio}  

\textbf{Tagline:} Red Team Operator | Web Builder | ML Explorer  

---

\section*{SECTION B: Incorporating Your Brand}

\subsection*{Part 1: Translating Your Brand}
Steps to ensure consistency across my website:
\begin{enumerate}
    \item Display my new tagline across all pages for brand clarity.
    \item Maintain a professional and unified tone in my Bio, portfolio, and contact section.
    \item Use consistent visuals — professional headshot, clean layouts, and matching icons.
    \item Keep the portfolio structure well-defined and pair it with easy-to-access contact links for visitors.
\end{enumerate}

\subsection*{Part 2a: Updating My Website}
3 changes I made for consistency:
\begin{enumerate}
    \item Added my new tagline and updated Bio to strengthen my personal brand.
    \item Uploaded a professional headshot to create a polished impression.
    \item Improved the site with easy contact links and a well-defined portfolio layout.
\end{enumerate}

\subsection*{Part 2b: Sharing My Website}
\href{https://sites.google.com/view/abdulmujeeb-uthman}{My Website}

---

\section*{SECTION C: Your Elevator Pitch}

\subsection*{Elevator Pitch Script}
``Hi, my name is Abdulmujeeb. I’m a Red Team Operator passionate about offensive security, penetration testing, and building secure systems. I also explore web development and machine learning, which give me a unique perspective on both creating and protecting digital solutions. I learn from industry experts and constantly build labs, projects, and CTF write-ups to sharpen my skills. My goal is to use Technology and Innovation to strengthen organizations against cyber threats while continuing to explore new ways of solving problems. Thank you.''  

\textbf{Elevator Pitch Video URL:} *(insert link after upload)*

---

\section*{SECTION D: Presenting Your Website}

\subsection*{Top 4 Things My Peers Liked About My Website}
\begin{enumerate}
    \item The clean and professional layout made the website easy to navigate.
    \item The new tagline and updated bio clearly presented my identity and skills.
    \item The professional headshot gave the site a polished and credible look.
    \item The portfolio section was well-structured and showed a variety of skills (cybersecurity, web building, ML exploration).
\end{enumerate}

\subsection*{Top 4 Suggestions My Peers Gave for Improvement}
\begin{enumerate}
    \item Add a stronger homepage introduction to quickly capture attention.
    \item Provide more detailed descriptions for each project (tools, process, outcomes).
    \item Ensure design consistency across all pages (fonts, colors, spacing).
    \item Make the contact section more accessible with clickable links or a simple form.
\end{enumerate}

\subsection*{Changes I Made After Feedback}
\begin{enumerate}
    \item Enhanced the homepage introduction with a clear tagline and short bio.
    \item Expanded portfolio descriptions to explain tools used and lessons learned.
    \item Improved design consistency by standardizing fonts, spacing, and color scheme.
    \item Updated the contact section with direct clickable links for easier communication.
\end{enumerate}

---

\section*{SECTION E: Your Skills}

\subsection*{Part 1: Skills Map}
\href{https://docs.google.com/spreadsheets/d/11I4psjQQPlH0mAMf97CslEBP5pNX6FJ0gSnHmt1YgX4/edit?gid=204951133\#gid=204951133}{My Updated Skills Map}

\subsection*{Part 2: Reflection}
Through this course, I strengthened several of my initial skills — especially communication, problem-solving, and time management. I also developed new skills I hadn’t expected, such as personal branding, portfolio building, and practical cybersecurity techniques.  

Compared to the start of the program, I now feel much more confident in my technical and professional abilities. I can articulate my strengths, showcase my projects, and map my career path clearly.  

I plan to keep developing my skills through continuous learning: building cybersecurity labs, joining Capture the Flag challenges, expanding my web and ML projects, and regularly updating my portfolio. The skills map has been a valuable tool to track my progress, and I’ll continue using it to stay accountable and measure growth.

\end{document}
